\documentclass{article}

\usepackage[margin=1in]{geometry}

\begin{document}

		\title{REPORT ON SURVEY OF BUS PROPOSAL}
		\author{PREPARED BY WACA DAVID}
		\date{Student No: 215001689}
		\maketitle
	
	\tableofcontents

\section{EXECUTIVE SUMMARY}
The students of Makerere University have a server parking problem, which has developed recently along with the increased numbers of students being admitted and having cars. Our department proposed having an excellent bus system to solve the problem, but we wanted to hear what students thought. We conducted the following survey, and the results are given below, along with our recommendations.

\section{INTRODUCTION}
A few years ago, parking for cars was not a problem at Makerere University. Recently, though, (about the last two years), this has become a serious problem with lateness accidents, damage and frustration resulting from over crowding of vehicles at the University.

Our department decided to implement a bus system for students and conducted a survey of all the levels of students from orientation to graduate, to determine their feelings and the best way to serve them students’ needs. The survey took one year since our admission at the University and the results are in the next section.

\section{SURVEY RESULTS}
The attached survey questionnaire give the details of the actual questions the students were asked. For all questions, either a response of excellent, Very Good, Good, Neutral, or Poor.

With numbers 1 to 7 were asked for. The questions ranged from (and then continue with the remainder of the explanation in details).
Here is a table that explains the results of the survey in a brief format.

\section{CONCLUSSION}
As a matter of conclusion, the implementation of a bus system to carry students from their respective holes and hostels would be good in the way that bus systems do not need spaces for parking as they always leave students at specific collages and at times on some stopping stations other than students coming with their private vehicles which will demand spaces for parking yet the University land is too little that it can not accommodate very many vehicles.

\section{RECOMMENDATIONS}
As a result of this study, here are the recommendations:

\begin{itemize}
\item {Bus system developed should starts working immediately from April 2017.}
\item {Parking spaces shall only be reserved for University Officials in order to reduce space wastage by student.}
\item {Parking spaces shall be given to students but at a cost of 5000 per hour.}
\end{itemize}


\end{document}